Kamala Harris Rises as the 2024 Election Front Runner: A Poll-of-Polls Forecast

### 2024-10-22 paper/paper.qmd
idealized survey update

The proposed survey questionnarie design is provided in the following link:

>>>>

The proposed survey questionnarie design is provided in the following link: https://forms.gle/zQ8iJyPk3HhJYrKd9.

::: {.layout}
## Image Row

::: {.column width="1/5"}
![Survey Intro](../other/idealized_survey/survey_intro.png)
:::

::: {.column width="1/5"}
![Survey Questions 1](../other/idealized_survey/survey_q1.png)
:::

::: {.column width="1/5"}
![Survey Questions 2](../other/idealized_survey/survey_q2.png)
:::

::: {.column width="1/5"}
![Survey Questions 3](../other/idealized_survey/survey_q3.png)
:::

::: {.column width="1/5"}
![Survey Final Thanks](../other/idealized_survey/survey_outro.png)
:::
:::
